Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-07 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
finished the description of figures/RemoveBay.pdf
working on the introduction

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}
\newcommand{\tab}{Tab.~}
\newcommand{\figs}{Figs.~}
\newcommand{\eqs}{Eqs.~}
\newcommand{\sects}{Secs.~}
\newcommand{\tabs}{Tabs.~}
\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}

@@

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{1997}
\copyrightyear{2016}

@@

\begin{document}
\title{Continuous Generalization of Buildings by Growing and 
	Merging}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
We propose a method to continuously 
generalize buildings from a given start scale to a smaller goal scale. 
%
If several buildings are close to each other at the start 
scale, we bridge them by line segments and merge the several buildings into 
one 
building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. 
Then we grow the building to the target shape.
%
After finishing the growing, we can take the goal scale as the 
start scale and repeat the process.
\newline\indent
The advantages of our method are as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

>>>>

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Figure~}
\newcommand{\eq}{Equation~}
\newcommand{\sect}{Section~}
\newcommand{\tab}{Table~}
\newcommand{\figs}{Figures~}
\newcommand{\eqs}{Equations~}
\newcommand{\sects}{Sections~}
\newcommand{\tabs}{Tables~}
\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}

@@

%Conference
\acmConference[UrbanGIS'17]{International Workshop on Smart Cities and Urban 
Analytics}{November 2017}{Redondo Beach, California USA} 
\acmYear{2017}
\copyrightyear{2017}

@@

\begin{document}
\title{Continuous Generalization of Buildings \\ by Growing and Aggregating}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
We propose a method to continuously 
generalize buildings from a given start scale to a smaller goal scale. 
%
If several buildings are close to each other at the start 
scale, we bridge them by line segments and merge them into 
one 
building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. 
Then we grow all buildings to their target shapes.
%
After finishing the growing, we can take the goal scale as the 
start scale and repeat the process.
\newline\indent
The advantages of our method are as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010405.10010476.10010479</concept_id>
	<concept_desc>Applied computing~Cartography</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Applied computing~Cartography}

\keywords{multiple representation, zooming, simplification, buffer}

### 2017-09-07 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on the introduction

Digital maps such as Google Maps and OpenStreetMap support zooming by 
displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, continuous generalization aims to 
produce 
a sequence of maps with small incremental changes.
To realize continuous generalization, \citet{Sester2005_CG} discussed some 
generalization operators for buildings and proposed to morph a building 
between 
its forms at different levels. 
Morphing has been used to generate intermediate 
representations for two representations at different scales 
\citep{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
Also aiming at 
realize continuous generalization, \citet{Chimani2014_Eat} generated a good 
selection sequence for road networks, and 
\citet{Peng2017_AStar} tried to compute optimal aggregation sequences for 
land-cover areas.

When users zoom out on digital maps, buildings become closer with each other 
and buildings themselves become smaller. 
In order to make sure that the map is 
easily perceived \citep{Weibel1997}, small building should be eliminated, 
some building should be enlarged, and buildings close to each other should be 
aggregated.
Although algorithms of simplifying buildings have been studied, e.g., 
\citet{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
when we have to aggregate buildings simultaneously.
In order to aggregate, we should first group the buildings.

@@

The papers we may review:   
\citet{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},

Rules for building simplification; see \citet{Lee2005}

Straight skeletons for map generalization: 
\citet{Gold2003,Matuk2006}

An example of enlargement in aggregation: \citet{Neun2005}

\section{Methodology}

\todo[inline]{a brief introduction of our method.}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$, 
the goal map when $t=1$, 
and that the start map is continuously generalized into the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \citet{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

@@

\subsection{Group buildings based on buffering}
\label{sec:Group}
We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove a such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

@@

\subsection{Merge close buildings by introducing bridges}
\label{sec:Merge}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

\subsection{Generate the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We group (see \sect\ref{sec:Group}) 
and merge (see \sect\ref{sec:Merge}) buildings on start map.
Then we grow (see \sect\ref{sec:Grow}) 
and simplify (see \sect\ref{sec:Simplify}) the merged buildings.
See for example \fig\ref{fig:Buffer_MiterLimits}, 
the building at time $t=1$ is the goal form of the three buildings of $t=0$.

\subsection{Generate buildings on intermediate maps}
\label{sec:Unite}

@@

\subsection{Eliminate small buildings}
\label{sec:Eliminate}
We eliminate a building if the area of this building is smaller than a 
threshold.
For a group of buildings, we consider the area sum of all the buildings.

@@

\section{Conclusions}
\label{sec:Conclusions}

>>>>

Digital maps such as Google Maps and OpenStreetMap 
support zooming by displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, 
we try to produce a sequence of maps 
with small incremental changes.
This process is known as \emph{continuous generalization}.

A way to realize continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
and then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps have to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{mnwb-mpstc-08}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
Between corresponding points, 
straight-line trajectories are often used to interpolate.
\citet{Peng2013_LSA} investigated the problem of defining interpolate 
trajectories 
based on least squares adjustment.
Using morphing, \citet{Peng2016_Admin} continuously generalized between maps of 
administrative boundaries based on compatible triangulations.

Also aiming at continuous generalization,
\citet{Danciger2009} grew polygons when a map was zoomed out. Their method 
preserves polygons' topology, area-rations, and relative positions. 
\citet{Chimani2014_Eat} generated a selection sequence for road network.
They removed one road at each step while keeping the remaining roads connected.
\citet{Peng2017_AStar} computed optimal aggregation sequences 
for land-cover areas.

Buildings are important elements on maps.
There are many methods of generalizing buildings.
For example, \citet{haunertwolff2010} generalized a set of buildings 
without topological conflicts based an integer program. 
Their method minimizes the number of edges of all the buildings 
and guarantees that the errors are smaller than a user-defined tolerance.
\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
One advantage is that their method preserves orientations of the edges.

When users zoom out on digital maps, 
buildings become smaller and the distance between buildings become smaller too. 
In order to make sure that the map is easily perceived, 
an objective proposed by \citet{Weibel1997}, 
some building should be enlarged,
and buildings close to each other should be aggregated.
The process of enlarging and aggregating can be used as a new way 
to compute urban settlement boundaries as did by
\citet{Chaudhry2008}, 
who identified the boundaries based on calculating 'citeness'.
If we have to consider enlarging, simplifying, 
and aggregating buildings simultaneously,
the continuous generalization becomes more complicated.

In our method,

@@

The papers we may review:   
\citet{vanSmaalen2003, Stoter2009},

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we generalize buildings on a start map to obtain buildings on a goal map 
by growing and merging. 
We simplify the buildings on the 
Using the start map and the goal map,
we generate maps at intermediate scales.

a workflow based on compatible
triangulations for generalizing administrative boundaries in a continuous and 
topologically
consistent way; see Section 2.We do a thorough case study with the boundaries
of the counties and the provinces of Mainland China to test the effectiveness
and the efficiency of our method; see Section 3. We conclude in Section 4.

\section{Methodology}
\label{sec:Methodology}
\todo[inline]{a brief introduction of our method.}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$, 
the goal map when $t=1$, 
and that the start map is continuously generalized into the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\subsection{Simplifying grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \citet{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
There are many ways to group buildings.

We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove a such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

@@

\subsection{Merging close buildings by introducing bridges}
\label{sec:Merge}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

\subsection{Generating the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We group (see \sect\ref{sec:Group}) 
and merge (see \sect\ref{sec:Merge}) buildings on start map.
Then we grow (see \sect\ref{sec:Grow}) 
and simplify (see \sect\ref{sec:Simplify}) the merged buildings.
See for example \fig\ref{fig:Buffer_MiterLimits}, 
the building at time $t=1$ is the goal form of the three buildings of $t=0$.

\subsection{Generating buildings on intermediate-scale maps}
\label{sec:Unite}

@@

\subsection{Eliminating small buildings}
\label{sec:Eliminate}
We eliminate a building if the area of this building is smaller than a 
threshold.
For a group of buildings, we consider the area sum of all the buildings.

@@

\section{Conclusion}
\label{sec:Conclusions}
